%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{hyperref}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}


\name{Kevin J. Turkington} % Your name

\address{} % Your address

%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)

\address{
  (+1)~503~709~4703
  \\ \href{mailto:TurkingtonKevin@gmail.com}{TurkingtonKevin@gmail.com} 
  \\ \href{www.KevinTurkington.com}{www.KevinTurkington.com}
}

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

  \begin{rSubsection}{\href{http://cass.oregonstate.edu/}{Center for Applied Systems and Software}}{March 2016 - Present}{Junior Software Developer}{}
  \item Worked in large development teams as a junior developer on projects for the Oregon  Department of Transportation and Smarter Balanced.
  \end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Oregon State University} \hfill {Fall 2014 - Spring 2018} 
\\ Computer Science, B.S

{\bf Center for Advanced Learning Charter School} \hfill {Fall 2013 - Spring 2014} 
\\ Computer Science Branch

{\bf Mt. Hood Community College} \hfill {Fall 2010 - Summer 2015} 
\\ Dual Enrollment

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills \& Coursework}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} p{4in} }

  Programming Languages &  C/C\#, Python, TypeScript, HTML, CSS, \LaTeX  \\

  Frameworks & React, MVC, ASP.NET, NodeJs \\

  Coursework & Web Development, Data Structures, Operating Systems I/II, Fundamentals of Software Engineering I/II\\

  Miscellaneous skills & Agile software development, Git workflow\\

  Operating Systems & Windows 7/10, Arch Linux, Ubuntu \\

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	Clubs and Projects SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Clubs \& Projects}
  
  \begin{rSubsection} {\href{http://osuusli.com}{NASA University Student Launch Initiative}} {Fall 2017 - Spring 2018} {Rover Programmer} {}
  \item Designed and programmed the software of the OSU USLI competition rover while conducting educational outreach sessions with local schools and maintained the team website.
  \end{rSubsection}

  \begin{rSubsection} {\href{http://sampleitems.smarterbalanced.org}{Smarter Balanced Sample Items}} {Summer 2017 - Present} {Sample Items Website} {}
  \item Refactored, added features, and web accessibility for the Smarter Balanced websites used by 4700 educators and 600,000+ students across the United States to compare individual students' academic performance on a national level.
  \end{rSubsection}

  \begin{rSubsection} {Oregon Department of Transportation} {Spring 2016 - Summer 2017} {TOCS Resource Management} {}
  \item Maintained, refactored, and updated the Transportation Operations Center System code base. This system coordinates emergency response teams to decrease response times for accidents and other disasters.
  \end{rSubsection}

  \begin{rSubsection} {\href{https://www.npmjs.com/package/@osu-cass/sb-components}{SB-components}} {Fall 2017} {} {}
  \item Created react modules for and maintained an NPM downloadable used for controlling and displaying information for the Smarter Balanced Websites.
  \end{rSubsection}

  \begin{rSubsection} {American Society of Mechanical Engineers} {Winter 2016 - Winter 2017} {WebMaster} {}
  \item Maintained and updated club website.
  \end{rSubsection}

\end{rSection}

\end{document}
